---
title: "Correlation between satisficing items and maximizing, well-being, personality,
  and self-rumination"
author: "Gabriel Baník, Lenka Vargová"
date: "8/15/2020"
output: html_document
---

Correlation of satisficing items and other examined variables (as was suggested in the review)

As well as maximizing, satisficing might also should be measured as a two-component model (as a goal and as a strategy). It seems that items (" If I am happy with my work, I do not seek better opportunities" [DMTI_las_1]) and (" I do not ask for more than what satisfies me" [DMTI_las_3]) are more related to “satisficing as a goal”, whereas items ("In choosing between alternatives, I stop at the first that works for me" [DMTI_las_2]) and ("When I watch TV or listen to the radio, I tend to follow the first program that I find interesting" [DMTI_las_4]) are more related to “satisficing as a strategy”. We inspect how items from satisficing are related to examined variables in the current study (see supplementary materials) and we found that item (" If I am happy with my work, I do not seek better opportunities" [DMTI_las_1]) was in a positive relationship with maximizing as a strategy, item ("In choosing between alternatives, I stop at the first that works for me" [DMTI_las_2]) was in a negative relationship with maximizing as a strategy, and item (" I do not ask for more than what satisfies me" [DMTI_las_3]) was in a negative relationship with maximizing as a goal. Different relationship of satisficing items and maximizing as a goal a and maximizing as strategy can point to suggestion to measure also satisficing as two-component model. On the other hand satisficing items were unrelated to every other examined variables which can appear to question the extent to which satisficing is a valid construct (in the sense of, for example, its criterion validity).

```{r include=FALSE}
library(readxl)
data <- read_excel("raw_data.xlsx")
```

```{r include=FALSE}
#load packages

library(tidyverse)
library(psych)
library(GPArotation)
library(mctest)
library(rockchalk)
library(apaTables)
library(lm.beta)
library(mice)
library(miceadds)
library(mitools)
library(corrplot)

####data preparation before exploratory analysis####

data <- data %>% 
  mutate_at("Gender", funs(recode(., `0`="male", `1`="female"))) %>% 
  mutate_at("Status", funs(recode(., `0`="single", `1`="in relationship", `2`="married", `3`="divorced"))) %>% 
  mutate_at("Education", funs(recode(., `0`="primary school", `1`="high school without graduation", `2`="high school with graduation", `3`="bachelor", `4`="master", `5`="doctoral"))) %>% 
  mutate_at("Type of data collection", funs(recode(., `0`="online", `1`="personal")))

##remove cases with more than 80% NA
data <- data[which(rowMeans(!is.na(data)) > 0.8), ]

#rename collumn type of data collection because of syntax error in the mice
data <- data %>% 
  rename(data_collection = 'Type of data collection')

#recode variables according to measures manual
data <- data %>% 
  mutate_at(c("BFI44_3", "BFI44_4", "BFI44_9", "BFI44_10", "BFI44_13", "BFI44_14",
              "RRQ_6", "RRQ_9", "RRQ_10"), 
            funs(recode(.,  `1`= 5, `2`=4, `3`=3, `4`=2, `5`=1))) %>%
  mutate_at("SHS_4", funs(recode(., `1`=7, `2`=6, `3`=5, `4`=4, `5`=3, `6`=2, `7`=1))) 

#imputation of missing
#object MICE
init <-   mice(data, maxit=0) 
meth <-   init$method
predM <-   init$predictorMatrix

predM[,c("Age", "Gender", "Status", "Education", "data_collection")] <-  0 #exclusion from the prediction
predM[c("Age", "Gender", "Status", "Education", "data_collection"),] <-  0 #exclusion from the prediction

meth[c("Gender", "Status", "Education", "data_collection")] <-  "" #exclusion from the imputation

set.seed(123)
data_imp <- mice(data, method=meth, predictorMatrix=predM, m=5, maxit = 10) #imputation of missing data - imputed object for the analysis

#convert mice object to list
data_list <- miceadds::mids2datlist(data_imp)

#####preparing total score of the variables on the list created from the 15 imputed variables

### total score and subscales 

#total score maximizing as a goal
data_list <- lapply(data_list, function(x){cbind(x, maximizing_goal = rowSums(x[,c("MTS7_1", "MTS7_2", "MTS7_3", "MTS7_4",
                                                                             "MTS7_5", "MTS7_6", "MTS7_7")], na.rm = TRUE))})
#total score maximizing as a strategy
data_list <- lapply(data_list, function(x){cbind(x, maximizing_strategy = rowSums(x[,c("MI_as_1", "MI_as_2", "MI_as_3", "MI_as_4",
                                                                                 "MI_as_5", "MI_as_6", "MI_as_7", "MI_as_8",
                                                                                 "MI_as_9", "MI_as_10", "MI_as_11", "MI_as_12")], na.rm = TRUE))})
#total score satisficing
data_list <- lapply(data_list, function(x){cbind(x, satisficing = rowSums(x[,c("DMTI_las_1", "DMTI_las_2", "DMTI_las_3", "DMTI_las_4")], na.rm = TRUE))})

#total score extraversion
data_list <- lapply(data_list, function(x){cbind(x, extraversion = rowSums(x[,c("BFI44_1", "BFI44_3", "BFI44_5",
                                                                          "BFI44_7", "BFI44_9", "BFI44_11", "BFI44_13",
                                                                          "BFI44_15")], na.rm = TRUE))})

#total score neuroticism
data_list <- lapply(data_list, function(x){cbind(x, neuroticism = rowSums(x[,c("BFI44_2", "BFI44_4", "BFI44_6",
                                                                         "BFI44_8", "BFI44_10", "BFI44_12", "BFI44_14",
                                                                         "BFI44_16")], na.rm = TRUE))})
#total score happiness
data_list <- lapply(data_list, function(x){cbind(x, happiness = rowSums(x[,c("SHS_1", "SHS_2", "SHS_3", "SHS_4")], na.rm = TRUE))})

#total score depression
data_list <- lapply(data_list, function(x){cbind(x, depression = rowSums(x[,c("BDI2_1", "BDI2_2", "BDI2_3",
                                                                        "BDI2_4", "BDI2_5", "BDI2_6", "BDI2_7",
                                                                        "BDI2_8", "BDI2_9", "BDI2_10", "BDI2_11",
                                                                        "BDI2_12", "BDI2_13", "BDI2_14", "BDI2_15",
                                                                        "BDI2_16", "BDI2_17", "BDI2_18", "BDI2_19",
                                                                        "BDI2_20", "BDI2_21")], na.rm = TRUE))})
#total score self_rumination
data_list <- lapply(data_list, function(x){cbind(x, self_rumination = rowSums(x[,c("RRQ_1", "RRQ_2", "RRQ_3",
                                                                        "RRQ_4", "RRQ_5", "RRQ_6", "RRQ_7",
                                                                        "RRQ_8", "RRQ_9", "RRQ_10", "RRQ_11",
                                                                        "RRQ_12")], na.rm = TRUE))})

#######transform list back to MICE object
data_imp <- miceadds::datlist2mids(data_list)

#complete all imputed dataset after lapply and create average values for variables from 15 imputed dataset (complete dataset according to Rubin's rule - Rubin (1987))
imp_complete <- mice::complete(data_imp, "long")
#maximizing_goal
imput1 <- imp_complete[1:514, "maximizing_goal"]
imput2 <- imp_complete[515:1028, "maximizing_goal"]
imput3 <- imp_complete[1029:1542, "maximizing_goal"]
imput4 <- imp_complete[1543:2056, "maximizing_goal"]
imput5 <- imp_complete[2057:2570, "maximizing_goal"]


data$maximizing_goal <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#maximizing_strategy
imput1 <- imp_complete[1:514, "maximizing_strategy"]
imput2 <- imp_complete[515:1028, "maximizing_strategy"]
imput3 <- imp_complete[1029:1542, "maximizing_strategy"]
imput4 <- imp_complete[1543:2056, "maximizing_strategy"]
imput5 <- imp_complete[2057:2570, "maximizing_strategy"]

data$maximizing_strategy <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#satisficing
imput1 <- imp_complete[1:514, "satisficing"]
imput2 <- imp_complete[515:1028, "satisficing"]
imput3 <- imp_complete[1029:1542, "satisficing"]
imput4 <- imp_complete[1543:2056, "satisficing"]
imput5 <- imp_complete[2057:2570, "satisficing"]

data$satisficing <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#extraversion
imput1 <- imp_complete[1:514, "extraversion"]
imput2 <- imp_complete[515:1028, "extraversion"]
imput3 <- imp_complete[1029:1542, "extraversion"]
imput4 <- imp_complete[1543:2056, "extraversion"]
imput5 <- imp_complete[2057:2570, "extraversion"]

data$extraversion <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#neuroticism
imput1 <- imp_complete[1:514, "neuroticism"]
imput2 <- imp_complete[515:1028, "neuroticism"]
imput3 <- imp_complete[1029:1542, "neuroticism"]
imput4 <- imp_complete[1543:2056, "neuroticism"]
imput5 <- imp_complete[2057:2570, "neuroticism"]

data$neuroticism <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#happiness
imput1 <- imp_complete[1:514, "happiness"]
imput2 <- imp_complete[515:1028, "happiness"]
imput3 <- imp_complete[1029:1542, "happiness"]
imput4 <- imp_complete[1543:2056, "happiness"]
imput5 <- imp_complete[2057:2570, "happiness"]

data$happiness <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#depression
imput1 <- imp_complete[1:514, "depression"]
imput2 <- imp_complete[515:1028, "depression"]
imput3 <- imp_complete[1029:1542, "depression"]
imput4 <- imp_complete[1543:2056, "depression"]
imput5 <- imp_complete[2057:2570, "depression"]

data$depression <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)
#self_rumination
imput1 <- imp_complete[1:514, "self_rumination"]
imput2 <- imp_complete[515:1028, "self_rumination"]
imput3 <- imp_complete[1029:1542, "self_rumination"]
imput4 <- imp_complete[1543:2056, "self_rumination"]
imput5 <- imp_complete[2057:2570, "self_rumination"]

data$self_rumination<- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)

#for correlation of satisficing items

#DMTI_las_1
imput1 <- imp_complete[1:514, "DMTI_las_1"]
imput2 <- imp_complete[515:1028, "DMTI_las_1"]
imput3 <- imp_complete[1029:1542, "DMTI_las_1"]
imput4 <- imp_complete[1543:2056, "DMTI_las_1"]
imput5 <- imp_complete[2057:2570, "DMTI_las_1"]

data$DMTI_las_1 <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)

#DMTI_las_2
imput1 <- imp_complete[1:514, "DMTI_las_2"]
imput2 <- imp_complete[515:1028, "DMTI_las_2"]
imput3 <- imp_complete[1029:1542, "DMTI_las_2"]
imput4 <- imp_complete[1543:2056, "DMTI_las_2"]
imput5 <- imp_complete[2057:2570, "DMTI_las_2"]

data$DMTI_las_2 <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)

#DMTI_las_3
imput1 <- imp_complete[1:514, "DMTI_las_3"]
imput2 <- imp_complete[515:1028, "DMTI_las_3"]
imput3 <- imp_complete[1029:1542, "DMTI_las_3"]
imput4 <- imp_complete[1543:2056, "DMTI_las_3"]
imput5 <- imp_complete[2057:2570, "DMTI_las_3"]

data$DMTI_las_3 <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)

#DMTI_las_4
imput1 <- imp_complete[1:514, "DMTI_las_4"]
imput2 <- imp_complete[515:1028, "DMTI_las_4"]
imput3 <- imp_complete[1029:1542, "DMTI_las_4"]
imput4 <- imp_complete[1543:2056, "DMTI_las_4"]
imput5 <- imp_complete[2057:2570, "DMTI_las_4"]

data$DMTI_las_4 <- round((imput1 + imput2 + imput3 + imput4 + imput5)/5, digits = 0)

```

```{r echo=FALSE}
###additional analysis after reviews
a <- cor(data[,c(25,26,27,28,82,83,85,86,87,88,89)])
corrplot(a)

miceadds::micombine.cor(data_imp, 
                        variables = c(25,26,27,28,82,83,85,86,87,88,89), 
                        conf.level=0.95, method="pearson", nested=FALSE, partial=NULL)

```

